---
title: "p8105_hw1"
author: "Dee Wang"
date: "29/09/2021"
output: github_document
---

Problem 1

Creating vectors. 

```{r}
library(tidyverse)

random_sample = rnorm(10, mean = 0, sd = 1)
logical_vector = c(random_sample > 0)
character_vector = c("a", "b", "c", "d", "e", "f","g","h","i","j")
factor_vector = c(-1, 0, 1, 0, 0, 1, 1, -1, -1, 1)
factor_vector = factor(factor_vector, levels = c(-1,0,1))

```

Next we will define the data frame containg random_sample, logical_vector, character_vector, factor_vector.

```{r}
data_frame = data.frame(random_sample, logical_vector, character_vector, factor_vector)
```

Next, we'll take the means of each variable in the dataframe.

```{r}
#taking means 
mean(pull(data_frame, random_sample)) 
mean(pull(data_frame, logical_vector)) 
mean(pull(data_frame, character_vector)) 
mean(pull(data_frame, factor_vector)) 
```

We couldn't take means of the character and factor vectors. We'll try applying the as.numeric function.

```{r take_mean, echo = T, results = "hide"}
as.numeric(pull(data_frame, logical_vector)) 
as.numeric(pull(data_frame, character_vector)) 
as.numeric(pull(data_frame, factor_vector)) 

```
After applying the as.numeric function, the trues in the logical vector are given '1' values and falses are given '0' values, so we can take the mean of logical vectors. NAs are introduced in the character vector and we are still unable to take a mean. The factor vector is able to be converted to numeric values and we can take the mean. 


